Indicators for Ecosystem Condition in Norway

### 2024-09-27 gjengroingMetaModel.Rmd
added functions to download airborne imagery

```{r}
wms_base_url <- 'https://wms.geonorge.no/skwms1/wms.nib?SERVICE=WMS&VERSION=1.1.1&REQUEST=GetMap&SRS=EPSG:25833'
output_dir <- "/data/P-Prosjekter2/412421_okologisk_tilstand_2024/Andrew/meta/HighResCanopyHeight-main/DataDownload/testHarstad/tiles"
metadata_url <- 'https://tjenester.norgeibilder.no/rest/projectMetadata.ashx'
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}
```

@@

##### Defining the area of interest
Here we include a shapefile of our area of intertest. The script will loop through all features in the shapefile, calculate their extent and query the WMS to download orthophotos within that extent in 256 x 256 pixel tiles. 
```{r}
ROIs <- vect("/data/P-Prosjekter2/412421_okologisk_tilstand_2024/Andrew/meta/HighResCanopyHeight-main/DataDownload/testHarstad/aoi.shp")
RegionPolygonUTM33N <- st_as_sf(ROIs)
if (st_crs(RegionPolygonUTM33N)$epsg != 25833) {
  RegionPolygonUTM33N <- st_transform(RegionPolygonUTM33N, crs = 25833)
}

@@

# Use mclapply for parallel processing
mclapply(1:nrow(RegionPolygonUTM33N), function(i) {
  geometry <- RegionPolygonUTM33N[i, ]
  id_field <- RegionPolygonUTM33N$id[i]  # Adjust field name if necessary
  fn.getOrtoImages(geometry, id_field, output_dir)
}, mc.cores = numCores)
```

>>>>

```{r}
wms_base_url <- 'https://wms.geonorge.no/skwms1/wms.nib?SERVICE=WMS&VERSION=1.1.1&REQUEST=GetMap&SRS=EPSG:25833'
output_dir <- "data/encroachment/metamodel/tiles"
metadata_url <- 'https://tjenester.norgeibilder.no/rest/projectMetadata.ashx'
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}
```

@@

##### Defining the area of interest
Here we include a shapefile of our area of intertest. The script will loop through all features in the shapefile, calculate their extent and query the WMS to download orthophotos within that extent in 256 x 256 pixel tiles. The AOI shape file should be in EPSG:25833 
```{r}

AOIs <- sf::st_read("data/encroachment/metamodel/AOIs.shp")

@@

# Use mclapply for parallel processing
mclapply(1:nrow(AOIs), function(i) {
  geometry <- AOIs[i, ]
  id_field <- AOIs$id[i]  # Adjust field name if necessary
  fn.getOrtoImages(geometry, id_field, output_dir)
}, mc.cores = numCores)
```

OK, now that we have our tiles, we can pass them to the canopy height model please see https://github.com/facebookresearch/HighResCanopyHeight for more details on the model.
